\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\input{glyphtounicode}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    {\Huge \scshape Khalid Alansary} \\ \vspace{1pt}
    New Cairo, Egypt \\ \vspace{1pt}
    \small \href{tel:+201204002811}{\raisebox{-0.1\height}\faPhone\ \underline{+201204002811}} ~ \href{mailto:khaled.ansary2003@outlook.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{khaled.ansary2003@outlook.com}} ~ 
    \href{https://www.linkedin.com/in/khalidalansary/}{\raisebox{-0.2\height}\faLinkedin\ \underline{KhalidAlansary}}  ~
    \href{https://github.com/khalidAlansary/}{\raisebox{-0.2\height}\faGithub\ \underline{KhalidAlansary}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Ain Shams University}{}
      {Bachelor of Science in Computer and Systems Engineering}{Sep. 2021 -- June 2026}
      \resumeItemListStart
        \resumeItem{\textbf{Relevant Coursework:} Data Structures, Algorithms, Database Systems, Software Engineering, Networks}
        \resumeItem{\textbf{Academic Projects:}}
        \begin{itemize}
          \item \small{\href{https://github.com/KhalidAlansary/Jelato}{\textcolor{blue}{\underline{Online Marketplace}}}} $|$ \emph{TypeScript, React, Supabase, PostgreSQL, Tailwind CSS}
          \begin{itemize}
            \item A full-stack marketplace app with user authentication, product listings, and transactions between users.
          \end{itemize}
          \item \small{\href{https://github.com/KhalidAlansary/tiny-parser}{\textcolor{blue}{\underline{Tiny Language Parser}}}} $|$ \emph{C, C++, Qt, Graphviz}
          \begin{itemize}
            \item Developed a compiler frontend with a GUI that generates a parse tree for the Tiny programming language.
          \end{itemize}
          \item \small{\href{https://github.com/KhalidAlansary/ugly-duckling}{\textcolor{blue}{\underline{Multipurpose XML Utility}}}} $|$ \emph{C++ (with boost library), Qt, Graphviz}
          \begin{itemize}
            \item A desktop application that validates and formats the XML, converts it to JSON, fixes misplaced tags, visualizes the XML data, along with various other features.
            \item Applied suitable data structures and algorithms for representing and manipulating the XML internally.
          \end{itemize}
          \item \small{\href{https://github.com/KhalidAlansary/Charity}{\textcolor{blue}{\underline{Charity Management System}}}} $|$ \emph{Docker, PHP, PostgreSQL, HTMX}
          \begin{itemize}
            \item Multi-Page site with PHP with focus on applying good design patterns such as the MVC pattern.
            \item Containerized the project with each component in its own container for robust and extensible development and deployment.
          \end{itemize}
        \end{itemize}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Ezz Steel}{July 2024}
      {Industrial Automation and IT Summer Internship}{Ain Sokhna, Suez}
      \resumeItemListStart
        \resumeItem{Created Python scripts that normalize CSV files to facilitate importation into the Oracle database.}
        \resumeItem{Acquired proficiency in server and network management, and security protocols, by implementing user-specific privileges on the company network.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}


%-----------CERTIFICATIONS-----------
\section{Certifications}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\href{https://www.credly.com/badges/a2c4111c-d3f4-4850-ae99-361e7489ac06}{\textcolor{blue}{\underline{\textbf{GitHub Foundations certification}}}} $|$ \emph{Git, GitHub}}{March 2025}
      \resumeProjectHeading
          {\small Validated proficiency in Git version control, collaborative workflows, and GitHub platform features.}{}
    \resumeSubHeadingListEnd



%-----------PROJECTS-----------
\section{Courses \& Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
      {\href{https://github.com/KhalidAlansary/Vencord}{\textcolor{blue}{\underline{\textbf{Vencord (Discord) Global Keybinds Plugin}}}} $|$ \emph{TypeScript, ElectronJS, NodeJS, Linux}}{June 2025}
      \resumeItemListStart
        \resumeItem{A Discord plugin that fixes global keybinds not working on Linux (and other Unix-like systems) running on Wayland by implementing XDG Global Shortcuts Portal using interprocess communication with dbus on Linux.}
      \resumeItemListEnd
      \resumeProjectHeading
          {\href{https://scrimba.com/certificate-cert2JbLs3qgAvqsGYGNk8Lo7ZwuaExT36m3wCB6rR}{\textcolor{blue}{\underline{\textbf{Scrimba's Advanced React course}}}} $|$ \emph{React, Javascript, HTML, CSS}}{March 2025}
          \resumeItemListStart
            \resumeItem{Implemented reusability patterns and custom hooks for state management in an e-commerce application.}
            \resumeItem{Built client-side routing with protected routes and integrated Firebase for authentication and database operations.}
            \resumeItem{Applied performance optimization techniques including memoization and lazy loading for complex applications.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\href{https://certificates.cs50.io/b41cb19f-0117-4da6-af42-80cfa762c907.pdf}{\textcolor{blue}{\underline{\textbf{HarvardX: CS50’s Introduction to Databases with SQL}}}} $|$ \emph{SQL, SQLite, MySQL, PostgreSQL}}{Feb. 2024}
          \resumeItemListStart
            \resumeItem{Learned how to create, read, update, and delete data using SQL commands. Gained practical experience with various database management systems, such as SQLite, MySQL, and PostgreSQL.}
            \resumeItem{\textbf{\href{https://github.com/KhalidAlansary/CS50SQL-Final-Project}{\textcolor{blue}{\underline{Final Project:}}}} Developed a database application to manage a library system, including features for book checkouts, returns, and user management. Utilized advanced SQL queries and optimized database performance.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\href{https://credentials.edx.org/credentials/a45ff39483ed4a8db7a6a667b469e3f8}{\textcolor{blue}{\underline{\textbf{HarvardX: Computer Science for Artificial Intelligence}}}} $|$ \emph{Python, TensorFlow, Algorithms}}{Aug. 2023}
          \resumeItemListStart
            \resumeItem{Gained exposure to the theory behind graph search algorithms, classification, optimization, reinforcement learning, and other topics in artificial intelligence and machine learning}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: JavaScript, TypeScript, Go, HTML/CSS, Rust, Java, SQL, Python, PHP, C/C++, Bash/Shell scripting} \\
     \textbf{Frameworks}{: Svelte, React, NextJS, Node.js, HTMX, Flask, Django, Qt} \\
     \textbf{Developer Tools}{: Git, Github, Github actions, Docker, Linux, Vim, CMake, VS Code} \\
     \textbf{Libraries}{: Tanstack Query (FKA React Query), shadcn, Boost, tkinter, pytest, pandas, NumPy, Matplotlib}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
